Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-09-07 revision/gloaguenNmfTraffic_v2.tex
proofread after ML

The TI-NMF behavior, with a threshold $t = 0.41$ and $\beta$ = 1, generates smaller errors compared to the baseline for all the $TIR$ values, with the exception at $TIR$ = 0 dB. \ml{pas clair: Its behavior is singular because it does not propose on each $TIR$ the lowest error} even if it is the best approach on all the corpus. Unlike Sup-NMF, where $\mathbf{W}$ is fixed, and Sem-NMF, where only $\mathbf{W_r}$ is updated, TI-NMF updates $\mathbf{W}$ entirely to adjust prior knowledge to the scene under evaluation so as to adapt to the different sound environments. The closest elements of the traffic component defined in $\mathbf{W_0}$ are then extracted to deduce the traffic signal.

@@

The non negative matrix factorization framework has been considered to estimate the road traffic sound level in urban sound mixtures. We found that it is a well suited approach to these sound environments because it easily takes into account the overlap between the multiple sound sources present in the cities and it is adapted to monophonic sensor networks. Different versions of NMF have been studied as a supervised and semi-supervised approach. On a large corpus of sounds, the supervised approach proves to be too restrictive to be adapted to different sound environments whereas the semi-supervised approach has, on the contrary, too many degrees of freedom on the mobile dictionary $\mathbf{W_r}$, decreasing its performance especially when the traffic is predominant. The proposed approach, named threshold initialized NMF achieves the lowest average error on the entire corpus. With this method, the $\mathbf{W}$ is initialized with road traffic spectra, updated and the dictionary elements that are similar to the road traffic spectra are then extracted by hard thresholding.
The study of the error according each $TIR$ reveals that this method is not the most efficient on each $TIR$, but it has to be remind that, this parameter is not available in practical case. TI-NMF can be considered as the approach that limit the error in the different environment. \ml{a reecrire ici et dans les resultats, les conditions de TIR les plus souvent vue c'est ca, et pour ces modes pris dans leur ensemble, la TI est celle qui marche le mieux.}

A major advantage of the proposed approach is that it is not designed for a specific source. Extending the proposed approach to other sources is also of interest for future research. The method should thus be tested and validated further on a larger and more diverse dataset with, for instance, motorcycles and other noisy traffic elements which are not considered in this study. Furthermore, even if the experiments described in this paper focused on road traffic level detection, changing the dictionary to contain bird sounds would lead to an estimator of the presence of birds.

 %Also, performance improvement could be achieved by the addition of constraints such as sparsity \cite{hoyer2004non} and smoothness \cite{virtanen_monaural_2007} of the low rank matrices.

>>>>

The TI-NMF behavior, with a threshold $t = 0.41$ and $\beta$ = 1, generates smaller errors compared to the baseline for all the $TIR$ values, with the exception at $TIR$ = 0 dB. If this approach gives the lowest error on all the corpus, it is not the one that propose on each $TIR$ the best performances: SUP-NMF has lower errors for positive $TIR$ while SEM-NMF surpasses it for $TIR \in \left\lbrace -12, -6\right\rbrace$. But the specific case $TIR = -12 dB$ is a less likely limit case in urban environment. Putting this specific case aside, TI-NMF is the only approach that propose an error inferior to 3 dB for $TIR \in \left\lbrace -6, 12 \right\rbrace$ dB. Unlike Sup-NMF, where $\mathbf{W}$ is fixed, and Sem-NMF, where only $\mathbf{W_r}$ is updated, TI-NMF updates $\mathbf{W}$ entirely to adjust prior knowledge to the scene under evaluation so as to adapt to the different sound environments. The closest elements of the traffic component defined in $\mathbf{W_0}$ are then extracted to deduce the traffic signal.

@@

The non negative matrix factorization framework has been considered to estimate the road traffic sound level in urban sound mixtures. We found that it is a well suited approach to these sound environments because it easily takes into account the overlap between the multiple sound sources present in the cities and it is adapted to monophonic sensor networks. Different versions of NMF have been studied as a supervised and semi-supervised approach. On a large corpus of sounds, the supervised approach proves to be too restrictive to be adapted to different sound environments whereas the semi-supervised approach has, on the contrary, too many degrees of freedom on the mobile dictionary $\mathbf{W_r}$, decreasing its performance especially when the traffic is predominant. The proposed approach, named threshold initialized NMF achieves the lowest average error on the entire corpus. With this method, the $\mathbf{W}$ is initialized with road traffic spectra, updated and the dictionary elements that are similar to the road traffic spectra are then extracted by hard thresholding.
The study of the error according each $TIR$ reveals that this method is not the most efficient on each $TIR$. But it should be remind that one case, $TIR$ = -12 dB, is a rarer case than other values in an urban environment and is intended to test the performance limitations of the NMF TI. If this case was putted aside, TI-NMF reveals to be the only method to reach an $MAE$ error inferior  to 3 dB. The MAE error in Table 2 would decrease to 1.39 while SEM NMF would be 2.15 and the baseline would be 1.77. Consequently, for an urban application where the $TIR$ is an unknown information, TI NMF seems to be the most suited version. 
A major advantage of the proposed approach is that it is not designed for a specific source. Extending the proposed approach to other sources is also of interest for future research. The method should thus be tested and validated further on a larger and more diverse dataset with, for instance, motorcycles and other noisy traffic elements which are not considered in this study. Furthermore, even if the experiments described in this paper focused on road traffic level detection, changing the dictionary to contain bird sounds would lead to an estimator of the presence of birds.
